A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-08 main.tex
PCA

%discussion: the third limitation
There are eighty one ($X_1 ... X_81$) physical, pathological and social features of patients available for survival modelling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. However, the TCGA did not collect other holistic features from their participants.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equal important comparing with physical and social status.
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
First principle is holistic – focusing on physical, socioeconomic, mental and emotional well-being. 
Holistic care: care and see the person as a whole with psychological, social and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
Second principle is Empowering – supporting people to manage and take responsibility for their own health. 
Empowerment: the process of supporting people and communities to take control of their own health needs resulting, for example, in the uptake of healthier behaviours or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their own care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} or even more for cancer patient. Being mindful to patient’s mental health and emotional changes during the dental care. Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration. Learning to listen proactively.
Being aware of patient’s spiritual needs during/after treatment.
%Applying the holistic healthcare strategies, such as the shared decision making, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}

%% PCA and ECA
Therapeutic relationship is an essence towards spiritual care.
Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}.
The research implication is to investigate the relationship between the patient’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
Dealing with negative emotions. As the patient feels intense negative emotions of fear, despair, sadness and so on, it is not the patient-centred therapist’s task to try and remove these feelings: The task is simply to stay with the patient’s experiences. 
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}

@@

%% why holistic?
中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
養生和治療的原則:
一、某些病症可以透過食療而改善的會建議自行調養
二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
四、沒有一勞永逸的食療，不宜執著特定的食療神話
五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
六、認識自己身體的狀態比吸收營養資訊更重要
七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
情志養生 悲喜憂思苦 七情
人俯仰於天地之間
順從四季氣候變化
保養正氣陶冶性情
自我療癒身心靈疾病
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生
每位醫師都可以成為「創傷知情者」
幫助我們身邊的病患， 懂他的心靈創傷
讓他有安全感， 才有機會改變疾病的走向

@@

Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
Bruce Lipton: the biology of belief %信念的力量
placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。

@@

In personal history section of admission note (EHR for inpatient): 
< Habits >
　　　　-Tobacco:
　、　1.5　pack/day for　30　years
　　　　-Alcohol drinking:　Occasionally
　　　　-Betel nuts:　、　nuts/day for　30　years　
　　< Social/Economic Evaluation >
　　　　-Living condition:　Living with family
　　　　-Family support:　Well
　　　　-Main caregiver:　Spouse
　　　　-Financial support:　Sufficient
　　< Psychological Evaluation >
　　　　Stable
　　　　Suspected to be ” abuse ” or ”neglected victim” (if the answer is “Yes“ should be assisted by social workers)　No
　　< Spiritual Assessment >
　　　　Religion:　Nil
　　　　Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers?　No

how to do: once holistic feature available, graph convolutional neural network (GCNN) is mandatory: 以免 genomics 光芒萬丈

>>>>

%discussion: the third limitation
There are eighty one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modelling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features in holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equal important comparing with physical and social status.
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
First principle is holistic – focusing on physical, socioeconomic, mental and emotional well-being. 
Holistic care is defined that care and see the person as a whole with psychological, social and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
Second principle is empowering – supporting people to manage and take responsibility for their own health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviours or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their own care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} and cancer patient care\cite{Hulett2016}. 
Being mindful to patient’s mental health, emotional changes, socioeconomic during healthcare. %Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration. 
Learning to listen proactively.
Being aware of patient’s spiritual needs.
%Applying the holistic healthcare strategies, such as the shared decision making, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}
% mindfulness-based cognitive therapies [MBCT]
%%%% MBSR "念" 今天的心 專心才有幸福感(味覺嗅覺靈敏專心吃
Mindfulness-Based Stress Reduction (MBSR) program has been introduced by Jon Kabat-Zinn in 1979\cite{Niazi2011}. MBSR composes the contemplative, spiritually based Buddhist philosophy, which promotes the development of a nonjudgmental, accepting, and patient worldview and teaches relaxation through focused awareness on breathing during meditation. It employs (static) mindfulness meditation to alleviate suffering associated with physical, psychosomatic and psychiatric disorders.
%是1979年麻薩諸塞大學的榮譽教授Jon Kabat-Zinn => 佛教禪修的mindfulness 正念止觀（中譯建譯：自我覺察）帶入西方身心醫學及心理學領域。
The Chinese Qigong and Tai Chi, belonging to movement-meditative-breathing interventions, also encourage mindfulness and self-awareness.

%Search Inside Yourself was born at Google in 2007 when one of Google’s earliest engineers, Chade-Meng Tan, gathered a team of leading experts in mindfulness, neuroscience, leadership and emotional intelligence to develop an internal course for fellow Google employees lovingly called Search Inside Yourself (SIY).

% 目的與功效
%  出入息 呼吸念頭 回到覺知，不再被潛意識自動導航干擾情緒
%正念，放下二元評價 正念覺知 XAI saliency mapping and trustworthiness in deep learning
%覺知 漸入空性 Y=wX + bias
%解決情緒苦(七情) 四聖諦
%慈悲心 安心（情緒穩定）
%了卻見人苦的「慈悲心」易感者同理心 empathy
%道歉不是一段文字，不是一個儀式（療癒冤親債主來自慈悲心）
%冤親債主 決定不再影響環境 基因 expression，減少意外與疾病、癌症
A systematic review of spiritually based interventions and psychoneuroimmunological outcomes in breast cancer survivorship was reported by Hulett et al.\cite{Hulett2016}. 
%Objective This is a review of spiritually based interventions (eg, mindfulness-based stress reduction, MBSR) that utilized psychoneuroimmunological (PNI) outcome measures in breast cancer survivors. Specifically, this review sought to examine the evidence regarding relationships between spiritually based interventions, psychosocial-spiritual outcomes, and biomarker outcomes in breast cancer survivors. 
%Methods A systematic search of 9 online databases was conducted for articles of original research, peer-reviewed, randomized and nonrandomized control trials from 2005-2015. Data were extracted in order to answer selected questions regarding relationships between psychosocial-spiritual and physiological measures utilized in spiritually based interventions. Implications for future spiritually based interventions in breast cancer survivorship are discussed. Results Twenty-two articles were reviewed. 
%mindfulness-based cancer recovery (MBCR) 
Psychosocial stress is associated with cancer incidence and poor survival\cite{Chida2008}.
This impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Thus, cortisol is one of the most common (objective) outcome studied in psychoneuroimmunological (PNI) factors. % others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV
The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}. %  body-mind-spirit (BMS) group therapy in the Meaning in Life questionnaire (MLQ) including two sub-scales: MLQ-Presence and MLQ-Search.
% The MLQ [15] for measuring psychological well-being consists of two subscales: the 5-item MLQ-Presence subscale, measuring the subjective sense that one’s life is meaningful, and the 5-item MLQ-Search subscale, measuring the drive and orientation toward finding meaning in one’s life.
%Compared with control groups, intervention groups demonstrated positive mental health outcomes and improved or stable neuroendocrine-immune profiles, although limitations exist. %Design methods have improved with regard to increased use of comparison groups compared with previous reviews. There are few spiritually based interventions that specifically measure religious or spiritual constructs. Similarly, there are few existing studies that utilize standardized religious or spiritual measures with PNI outcome measures. 
Findings suggest that mindfulness-breathing-stretching interventions appear to offer potential improvement or stabilization of neuroendocrine-immune activity in breast cancer survivors compared to control groups.
This review revealed a positive pattern between spiritually based interventions and a number of PNI biomarker outcomes, suggesting that spiritually based interventions offer positive mental and physiological health benefits. For breast cancer survivors, these studies suggested that engaging in spiritually based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.
%From a PNI perspective, future spiritually based interventions should include standardized measures of religiousness and spirituality in order to understand relationships between and among religiousness, spirituality, and neuroendocrine-immune outcomes. Future research should now focus on determining the minimum dose and duration needed to improve or stabilize neuroendocrine-immune function, as well as 
%diverse setting needs, including tele-medicine practice for survivors who are too ill to travel to group sessions or lack economic resources.

% 自動導航（潛意識）易受情緒影響，造成焦慮、發炎、免疫 Cancer
%Mindfulness based stress reduction provides psychological benefit and restores immune function of women newly diagnosed with breast cancer: A randomized trial with active control.
%BACKGROUND: Women newly diagnosed with breast cancer experience psychological distress, accompanied by reduced Natural Killer Cell Activity (NKCA) and altered levels of cytokines, which may compromise cancer control. Few studies have evaluated psycho-immune outcomes of mindfulness-based stress reduction (MBSR) for women newly diagnosed with breast cancer in comparison to an active control condition. OBJECTIVE: The purpose of this study was to determine whether MBSR benefits psychological, behavioral, and immunological function in women recently diagnosed with breast cancer. DESIGN: After confirmation of breast cancer staging, women diagnosed with early-stage breast cancer (n = 192) were randomized to an 8-week MBSR program or an 8-week active control condition (ACC). The ACC consisted of a series of cancer recovery and health education classes. Both MBSR and the ACC were administered in group format. METHODS: Women completed psychometric instruments and provided blood for NKCA and cytokine levels at pre-, mid-, and completion of program, as well as at 1- and 6-months post-program. One hundred and twenty four women completed all five-assessments (MBSR, n = 63; ACC, n = 61). Hierarchical linear modeling was used to analyze trajectories of outcomes over time and between groups. 
%RESULTS: Compared to the ACC group, women randomized to MBSR exhibited decreasing trajectories of perceived stress, fatigue, sleep disturbance, and depressive symptoms. 
%Further, compared to women randomized to ACC, MBSR women exhibited trajectories demonstrating significantly more rapid restoration of NKCA, accompanied by 
%lower circulating TNF-alpha levels, lower IL-6 production =>  pro-inflammatory cytokines
%and greater IFN-gamma production => IFN gamma supports an immune-mediated response against cancer and this may be important during the transition following cancer treatment
A randomized clinical trial with active control proved that early provision of MBSR for women newly diagnosed with breast cancer provides psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) supportive of cancer survival.\cite{WitekJanusek2019}

%%%% PCA and ECA: the delivery of MBSR
Therapeutic relationship is an essence towards spiritual care.
Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}.
For constructive personality change to occur, it is necessary that these
conditions exist and continue over a period of time: 
1. Two persons are in psychological contact. 
2. The first, whom we shall term the client, is in a state of incongruence, being vulnerable or anxious. 
3. The second person, whom we shall term the therapist, is congruent
or integrated in the relationship. 
4. The therapist experiences unconditional positive regard for the client. 
5. The therapist experiences an empathic understanding of the client's
internal frame of reference and endeavors to communicate this experience to the client. 
6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.

%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of fear, depression, stress, anxiety, fatigue, sadness, it is not the patient-centred therapist’s task to remove these feelings: The task is simply to stay with the patient’s experiences. 
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}

@@

%% why holistic? 太極 氣功 情緒 myofascia and sympathetic system
中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
養生和治療的原則:
一、某些病症可以透過食療而改善的會建議自行調養
二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
四、沒有一勞永逸的食療，不宜執著特定的食療神話
五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
六、認識自己身體的狀態比吸收營養資訊更重要
七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
情志養生 悲喜憂思苦 七情
人俯仰於天地之間
順從四季氣候變化
保養正氣陶冶性情
自我療癒身心靈疾病
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生
每位醫師都可以成為「創傷知情者」
幫助我們身邊的病患， 懂他的心靈創傷
讓他有安全感， 才有機會改變疾病的走向

@@

Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.

gene expression in deep learning
Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).\cite{Ching2018}
%慈悲心 利他心
*** make Figure 5 holistic:
meridian and emotion has mutual reaction
meridian effect tissue and organ
(autonomic nerve system, myofascial network, prefrontal cortex)
placebo-effect influence on drug discovery
博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
#正念 除了可以減壓，還可以治癒疼痛
Environment 改造患者的心，就能改造他的身體環境，有利消除癌症

Bruce Lipton: the biology of belief %信念的力量
placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。

@@

In personal history section of admission note (EHR for inpatient): 
< Habits >
　　　　-Tobacco:
　、　1.5　pack/day for　30　years
　　　　-Alcohol drinking:　Occasionally
　　　　-Betel nuts:　、　nuts/day for　30　years　
　　< Social/Economic Evaluation >
　　　　-Living condition:　Living with family
　　　　-Family support:　Well
　　　　-Main caregiver:　Spouse
　　　　-Financial support:　Sufficient
　　< Psychological Evaluation >
　　　　Stable
　　　　Suspected to be ” abuse ” or ”neglected victim” (if the answer is “Yes“ should be assisted by social workers)　No
　　< Spiritual Assessment >
　　　　Religion:　Nil
　　　　Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers?　No
　　　　
　　　　suggested TCGA features:
cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors. Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
 psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) 
how to do: once holistic feature available, graph convolutional neural network (GCNN) is mandatory: 以免 genomics 光芒萬丈
